### 2016-05-05 ch02-qlogms/excitation-design.tex
(sub)+sections: title case + some \gls{...}

\subsection{General purpose robust excitation signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

@@

\section{Input design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ is a rational, time invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.

@@

\section{Logarithmic power distributions}
\label{sec:excitation:logarithmic}
When no information about the system is known, it is desirable that the excitation signal is such that regardless of the true system characteristics, the resulting estimates have equally good statistical properties.
This can be ensured by a suitable choice of the input power spectrum.

 \subsection{A second order system}
Consider the second order system
\begin{align}
y(t) 
  &= 
  G(s,\theta) u(t) 
  = \frac{1}
                {\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}
      u(t),
\label{eq:excitation:2ndOrderSys}
\end{align}
with parameters $\theta=[\wn\;\damping]^{\T}$. 
The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$.

@@

\subsection{Sums of second order systems}
This section extends the previous section to more general systems than second order.
Consider a system
\begin{align}
G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
             =\sum_{i=1}^{K}  \frac{1}
                                   {   \frac{s^2}{\wn[i]^2}
                                    + 2\frac{\damping[i]}{\wn[i]}s
                                    + 1},\\
\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
\label{eq:excitation:sumSys}
\end{align}
The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.

@@

\subsubsection{Example: Sum of two second-order systems}
\label{sec:excitation:ex:sumOfSecondOrderSipmle}
Consider the system
\begin{align}
G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)%\\
%&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\\damping[2]}{\wn[2]}s + 1},
\end{align}
with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
The information matrix for this system is
\begin{align}
\Fi{\theta} &=
       \begin{bmatrix}
         \partial G_{1,1}  & \partial G_{1,2}\\
         \partial G_{2,1}  & \partial G_{2,2}
       \end{bmatrix}.
\label{eq:excitation:infoEx}
\end{align}
To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.

@@

\section{System parametrization} 
\label{sec:excitation:parametrization}

@@

  \subsection{Comparison of the frequency grids}
  To gain some insight into these different grids, \figref{fig:excitation:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
  For this example, a frequency spacing $\Delta f = 1\unit{Hz}$ and frequency ratio $\alpha = 1.05$ are used.

@@

\section{Optimization of the frequency spacing} 
\label{sec:excitation:optimAlpha}
  \subsection{Calculation of the model uncertainty}
  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing $\alpha$, has not been designed.

@@

  \subsection{Relation between the frequency grid and the system resonance} 
  \label{sec:excitation:relationLogGridSystem}
  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated \glspl{FRF} of a set of prototype second-order systems excited by logarithmically spaced excitation signals.

@@

  \subsection{Exploiting the shape of the derivatives}
   In particular, from \figref{fig:excitation:derivatives}, it can be seen that the derivatives with respect to $(\wn, \damping)$ exhibit a sharper resonance and hence $(\wn, \damping)$ will prove the hardest to identify.
   This means that if one would design a signal to identify just $(\wn, \damping)$, such a signal would also be well-suited to identify the other parameters since their corresponding weight in the Fisher information matrix is very similar (especially in the vicinity of the resonance, where their amplitude is most significant).

@@

  \subsection{Selection of the frequency grid spacing $\alpha$}
  Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
  To deal with this, we introduce the normalized frequency ratio
  \begin{equation}
    \tilde{\alpha} = \frac{\alpha - 1}
                          {\damping}
                   \propto \frac{\omega_{k+1} - \omega_k}
                                {\wdB}
                           \cdot
                           \frac{\wn}{\omega_k}
    \text{.}
    \label{eq:excitation:normAlpha} 
  \end{equation}
  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:excitation:normAlpha} can safely be neglected.

@@

  \subsection{Systems with a `high' damping}
  To test the signals for systems with a high damping with respect to the frequency ratio in the excitation signal, systems with a damping $\damping = 0.2$ are used.
  White Gaussian noise $e[n]$ with a standard deviation $\sigma_e \approx 0.0678$ added to the output.

@@

  \subsection{Systems with a lower damping}
  Given the optimal frequency ratio \eqref{eq:excitation:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
  In this set of simulations, we check this by repeating the previous set for such systems.
  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the \gls{SNR} of $20\unit{dB}$.
  The corresponding results are shown in \figref{fig:excitation:damping005}.

@@

  \subsection{Simulation example on higher order systems}
To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:excitation:secondOrderSystemDTidentifiable} in parallel. This is equivalent to adding their respective transfer functions, therefore, the resulting transfer function is of the form:
\begin{equation}
  G \left( z \right) 
  = \frac{         b_4 z^{4} + b_3 z^{3} + b_2 z^{2} + b_1 z + b_0}%
         {\phantom{a_4}z^{4} + a_3 z^{3} + a_2 z^{2} + a_1 z + a_0}
  \text{.}
\label{eq:excitation:tfO4}
\end{equation}

>>>>

\subsection{General Purpose Robust Excitation Signals}
\label{sec:excitation:intro:approach}
In this chapter, the goal is to construct excitation signals that bridge the properties of general purpose and robust excitation signals to alleviate the chicken-and-the-egg problem that optimal strategies typically incur.
In particular, a generic excitation signal will be used, but its properties are tuned in such a way that it attains some properties of robust excitation signals without requiring extensive prior information.
We will consider input design when it is known that the system has resonances, possibly spanning a frequency band that may cover several decades. 
It is however not necessary to know how many resonances are in the system and at what precise frequencies those may occur.

@@

\section{Input Design}
\label{sec:excitation:inputDesign}
For the theoretical analysis, we consider \gls{SISO} \gls{OE} systems, i.e.
\begin{align}
y(t) &=G(s,\theta)u(t)  + e(t),
\end{align}
where $u(t)$ is a known input sequence, $y(t)$ the output sequence, and $e(t)$ is zero mean Gaussian white noise with variance $\sigma_{e}^2$.
$G$ is a rational, time invariant transfer function in continuous time.
For notational simplicity, $s$ is used both as the complex Laplace variable and the differentiation operator; it should be clear from the context which is used. 
The transfer function is parameterized by the vector $\theta$.
These parameters are unknown and hence we are interested in estimating their values.

@@

\section{Logarithmic Power Distributions}
\label{sec:excitation:logarithmic}
When no information about the system is known, it is desirable that the excitation signal is such that regardless of the true system characteristics, the resulting estimates have equally good statistical properties.
This can be ensured by a suitable choice of the input power spectrum.

 \subsection{A Second Order System}
Consider the second order system
\begin{align}
y(t) 
  &= 
  G(s,\theta) u(t) 
  = \frac{1}
                {\frac{s^2}{\wn^2} + 2\frac{\damping}{\wn}s + 1}
      u(t),
\label{eq:excitation:2ndOrderSys}
\end{align}
with parameters $\theta=[\wn\;\damping]^{\T}$. 
The resonance frequency of the system is $\wR \isdef \sqrt{1-\damping^2}\wn$.

@@

\subsection{Sums of Second Order Systems}
This section extends the previous section to more general systems than second order.
Consider a system
\begin{align}
G(s,\theta) &= \sum_{i=1}^{K} G_i(s,\theta_i)
             =\sum_{i=1}^{K}  \frac{1}
                                   {   \frac{s^2}{\wn[i]^2}
                                    + 2\frac{\damping[i]}{\wn[i]}s
                                    + 1},\\
\theta_i&=[\wn[i]\;\damping[i]]^{\T}.
\label{eq:excitation:sumSys}
\end{align}
The systems  $G_i$ will be called the \emph{sub-systems} of $G$. 
Without loss of generality, we assume that $\wn[1] < \wn[2] < \cdots < \wn[K]$. 
To properly identify the system $G$, excitation is required such that all subsystems are properly excited, regardless of their individual resonance frequencies.

@@

\subsubsection{Example: Sum of Two Second-Order Systems}
\label{sec:excitation:ex:sumOfSecondOrderSipmle}
Consider the system
\begin{align}
G(s,\theta) &= G_1(s,\theta_1) + G_2(s,\theta_2)\\
&=\frac{1}{\frac{s^2}{\wn[1]^2} + 2\frac{\damping[1]}{\wn[1]}s + 1} 
   + \frac{1}{\frac{s^2}{\wn[2]^2} + 2\frac{\damping[2]}{\wn[2]}s + 1},
\end{align}
with $\theta_1=[\wn[1]\;\damping[1]]^{\T}$ and $\theta_2=[\wn[2]\;\damping[2]]^{\T}$.
The information matrix for this system is
\begin{align}
\Fi{\theta} &=
       \begin{bmatrix}
         \partial G_{1,1}  & \partial G_{1,2}\\
         \partial G_{2,1}  & \partial G_{2,2}
       \end{bmatrix}
       \text{.}
\label{eq:excitation:infoEx}
\end{align}
To investigate the decoupling, we study the $(1,1)$ elements of blocks $\partial G_{1,1}$ and $\partial G_{1,2}$ of the information matrix \eqref{eq:excitation:infoEx}, when the input spectrum \eqref{eq:excitation:pink} is used; similar arguments can be made for the other elements of the two matrix blocks.

%FIXME: clean up latex math here, e.g. \frac{\partial ...}{\partial} -> \partialDerivative{...}{...}; use \abs{}; ...

@@

\section{System Parametrization} 
\label{sec:excitation:parametrization}

@@

  \subsection{Comparison of the Frequency Grids}
  To gain some insight into these different grids, \figref{fig:excitation:freqGrids} depicts the amplitude spectrum for a linear, log, compensated quasi-log and pink quasi-log grid multisine that all carry the same total power.
  For this example, a frequency spacing $\Delta f = 1\unit{Hz}$ and frequency ratio $\alpha = 1.05$ are used.

@@

\section{Optimization of the Frequency Spacing} 
\label{sec:excitation:optimAlpha}
  \subsection{Calculation of the Model Uncertainty}
  In the previous section logarithmically spaced multisines were introduced, but up to now their major parameter, the frequency spacing $\alpha$, has not been designed.

@@

  \subsection{Relation Between the Frequency Grid and the System Resonance} 
  \label{sec:excitation:relationLogGridSystem}
  To determine an appropriate frequency ratio $\alpha$ for a logarithmically spaced signal, we study the estimated \glspl{FRF} of a set of prototype second-order systems excited by logarithmically spaced excitation signals.

@@

  \subsection{Exploiting the Shape of the Derivatives}
   In particular, from \figref{fig:excitation:derivatives}, it can be seen that the derivatives with respect to $(\wn, \damping)$ exhibit a sharper resonance and hence $(\wn, \damping)$ will prove the hardest to identify.
   This means that if one would design a signal to identify just $(\wn, \damping)$, such a signal would also be well-suited to identify the other parameters since their corresponding weight in the Fisher information matrix is very similar (especially in the vicinity of the resonance, where their amplitude is most significant).

@@

  \subsection{Selection of the Frequency Grid Spacing $\Alpha$}
  Since the damping influences the $3\unit{dB}$ bandwidths, this will become important when one has to determine the grid spacing $\alpha$.
  To deal with this, we introduce the normalized frequency ratio
  \begin{equation}
    \tilde{\alpha} = \frac{\alpha - 1}
                          {\damping}
                   \propto \frac{\omega_{k+1} - \omega_k}
                                {\wdB}
                           \cdot
                           \frac{\wn}{\omega_k}
    \text{.}
    \label{eq:excitation:normAlpha} 
  \end{equation}
  This normalized frequency ratio can be interpreted as a measure of the grid resolution, relative to the $3\unit{dB}$ bandwidth of the second order system.
  The grid resolution in a (quasi-) log grid is $\left( \alpha - 1\right)\omega_k$ while the system bandwidth is approximately $2\damping\wn$.
  Around the resonance, $\omega_k \approx \wn$, such that the last fraction in \eqref{eq:excitation:normAlpha} can safely be neglected.

@@

  \subsection{Systems With a `High' Damping}
  To test the signals for systems with a high damping with respect to the frequency ratio in the excitation signal, systems with a damping $\damping = 0.2$ are used.
  White Gaussian noise $e[n]$ with a standard deviation $\sigma_e \approx 0.0678$ added to the output.

@@

  \subsection{Systems With a Lower Damping}
  Given the optimal frequency ratio \eqref{eq:excitation:optimAlpha}, one expects that quasi-logarithmic grids with a frequency ratio $\alpha = 1.05$ will allow to identify second order systems with damping $\damping = 0.05$ with a constant uncertainty.
  In this set of simulations, we check this by repeating the previous set for such systems.
  In this case, the output noise is chosen $\sigma_e \approx 0.1123$ to keep the \gls{SNR} of $20\unit{dB}$.
  The corresponding results are shown in \figref{fig:excitation:damping005}.

@@

  \subsection{Simulation Example on Higher Order Systems}
To show that the suggested method also works on more general systems, we considered a system that consists of two second order systems \eqref{eq:excitation:secondOrderSystemDTidentifiable} in parallel. This is equivalent to adding their respective transfer functions, therefore, the resulting transfer function is of the form:
\begin{equation}
  G \left( z \right) 
  = \frac{         b_4 z^{4} + b_3 z^{3} + b_2 z^{2} + b_1 z + b_0}%
         {\phantom{a_4}z^{4} + a_3 z^{3} + a_2 z^{2} + a_1 z + a_0}
  \text{.}
\label{eq:excitation:tfO4}
\end{equation}

### 2016-05-05 ch03-lrm/nonparametric.tex
(sub)+sections: title case + some \gls{...}

\section{Local modeling approaches}
\label{sec:theory}

@@

\subsection{Local modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\Sum_{i=0}^{\order{B}} b_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\Sum_{i=0}^{\order{C}} c_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

@@

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced by \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
  \label{eq:nparam:linearRegression}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
    \phantom{+}
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \phantom{+}
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    - \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    - \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

@@

\subsection{The Local Polynomial Method}
\label{sec:nparam:LPM}
The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.

@@

  % \subsection{Implications of the model structure}
  % \subsection{Implications of the noise coloring}

@@

\section{Trading off the bias and variance}
In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
This is specifically the case for small and noisy datasets.
Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}.
As such, it makes sense to ask ourselves the question: ``can we determine a good local model order''?
That is the question we will investigate in this section.
First, some classical approaches are compared in the context of local modeling, i.e. relatively small (local) datasets.

\subsection{Order selection}
\label{sec:nparam:orderSelection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

@@

\subsubsection{Combining different local model orders}
In the previous section, different methods were introduced to select the local model order.
This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
The answer to this, depends on the ultimate purpose of the \gls{FRF}.

>>>>

\section{Local Modeling Approaches}
\label{sec:theory}

@@

\subsection{Local Modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\Sum_{i=0}^{\order{B}} b_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\Sum_{i=0}^{\order{C}} c_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

@@

\subsection{The \glsentrydesc{LRM}}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced by \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
  \label{eq:nparam:linearRegression}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
    \phantom{+}
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \phantom{+}
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    - \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    - \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

@@

\subsection{The \glsentrydesc{LPM}}
\label{sec:nparam:LPM}
The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.

@@

  % \subsection{Implications of the Model Structure}
  % \subsection{Implications of the Noise Coloring}

@@

\section{Trading Off the Bias and Variance}
In the last section, it was illustrated that the model order of the local \gls{LRM} models, can significantly affect the obtained \gls{RMS} error.
This is specifically the case for small and noisy datasets.
Moreover, it was observed that the \gls{LRIC} has a high variance which might be due to pole-zero cancellations in the \gls{LRIC}.
As such, it makes sense to ask ourselves the question: ``can we determine a good local model order''?
That is the question we will investigate in this section.
First, some classical approaches are compared in the context of local modeling, i.e. relatively small (local) datasets.

\subsection{Order Selection}
\label{sec:nparam:orderSelection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

@@

\subsubsection{Combining Different Local Model Orders}
In the previous section, different methods were introduced to select the local model order.
This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
The answer to this, depends on the ultimate purpose of the \gls{FRF}.
